---
title: "hunter_or_prey"
author: "Asier Moneva"
date: "04/04/2020"
---

# Load packages

```{r}
library(tidyverse)
library(xlsx)
library(GGally)
```


# Load the dataset

```{r}
dataset <- read.xlsx(file = "path")
dataset_dv <- read.xlsx(file = "path")
```


# Data transformation

Create two subsets, one for offending and another for victimisation.

```{r}
# Offending matrix
dataset_offe <- as_tibble(dataset %>% 
  select(sex, age_, hours_, snapchat, instagram, facebook, twitter, name, photos, privacy, CHOffe)
  )

# Offending DV
dv_offe <- dataset_dv %>% 
  select(insulthumO, rumourO, threatO, IdentityO, marginO)

# Victimisation matrix
dataset_vict <- as_tibble(dataset %>% 
  select(sex, age_, hours_, snapchat, instagram, facebook, twitter, name, photos, privacy, CHVict)
  )

# Victimisation DV
dv_vict <- dataset_dv %>% 
  select(insulthum, rumour, threat, identity, margin)
```


# CACC analysis

Load the CACC function

```{r}
cacc <- function (data,
                 x = colnames(data[, - ncol(data)]),
                 y = colnames(data[, ncol(data)])) {

  # ------------------------------ Preprocessing -------------------------------
  # Check the dependent variable (DV):
  #   If it is not numeric, convert its values to numeric and replace them with
  #     0 / 1.
  #   If it is not binary, the function returns an ERROR.
  #   If it is binary:
  if (length(unique(data[[y]])) != 2) {
    stop ("ERROR. The dependent variable has to be binary")
  } else if (! is.numeric(data[[y]])) {
    print("ERROR. The dependent variable has to be numeric and binary.")
    print("Preprocessing...")

  #     Convert the variable into a factor,
    data[[y]] <- as.factor(data[[y]])

  #     Replace categories with 0 / 1.
    levels(data[[y]]) <- c(0, 1)
    print("Done.")

  #     Problem: if R understands that "No" > "Yes" then this variable gives the
  #     value "1" to "No" and "0" to "Yes".
  } else if (is.double(data[[y]])) {

  #       First, the variable must be converted into a integer.
    data[[y]] <- as.integer(data[[y]])

  #       Then, the variable must be converted into a factor.
    data[[y]] <- as.factor(data[[y]])

  #       Lastly, categories must be replaced with 0 / 1.
    levels(data[[y]]) <- c(0, 1)
  }

  # --------- Handle dominant profiles depending on predetermined size ---------
  if (nrow(data) < 1000) {
    dom_pro = 5
  } else {
    dom_pro = 10
  }

  # ------------------------- Generate the CACC matrix -------------------------
  # Generate a matrix with total frequencies.
  matrixT <- data %>%
    dplyr::count(.dots = x) %>%
    dplyr::arrange(desc(n)) %>%
    dplyr::rename(N_Break = "n")

  # Generate a matrix with DV frequencies based on the positive class (i.e. 1).
  matrix1 <- data %>%
    dplyr::filter(get(y) == 1) %>%
    dplyr::count(.dots = x) %>%
    dplyr::arrange(desc(n)) %>%
    dplyr::rename(N_1 = "n")

  # Calculate the probabilities for each dominant profile
  cacc_matrix <- dplyr::full_join(matrixT, matrix1,
                             by = x) %>%
    dplyr::mutate(p = N_1 / N_Break) %>%
    dplyr::filter(N_Break >= dom_pro) %>%
    dplyr::arrange(desc(p)) %>%
    dplyr::select(- one_of("N_1"))

  # Return the CACC matrix.
  return (cacc_matrix)
}
```

Conduct a CACC for each dataset

```{r}
# Victimisation CACC
cacc_matrix_vict <- cacc(data = dataset_vict)
cacc_matrix_vict$p[which(is.na(cacc_matrix_vict$p))] <- 0

# Central tendency statistics
mean(cacc_matrix_vict$p)
mean(cacc_matrix_vict$N_Break)
sd(cacc_matrix_vict$p)
sd(cacc_matrix_vict$N_Break)

# Offending CACC
cacc_matrix_offe <- cacc(data = dataset_offe)
cacc_matrix_offe$p[which(is.na(cacc_matrix_offe$p))] <- 0

# Central tendency statistics
mean(cacc_matrix_offe$p)
# mean(cacc_matrix_offe$N_Break)
sd(cacc_matrix_offe$p)
# sd(cacc_matrix_offe$N_Break)
```


# Chi-square analysis

Load the Chi-square function

```{r}
cacc_xsq <- function (cacc_matrix){
  #If the Break variable does not exist, cacc matrix is calculated.
  if(("N_Break" %in% names(cacc_matrix)) == FALSE){
    cacc_matrix <- cacc(cacc_matrix)
    print("CACC matrix has been calculate")
  }

  # Declare the variable containing the number of times each dominant profile is
  #   observed in the sample.
  obs <- cacc_matrix$N_Break

  # Count the dominant profiles observed.
  N_obs <- nrow(data.frame(obs))

  # Obtain the expected count vector by weighting the total amount of dominant
  # observations by the amount of dominant profiles observed.
  exp <- rep(sum(obs) / N_obs, N_obs)

  # Perform the Chi-square test.
  # rescale.p = TRUE because probabilities must sum 1.
  xsq <- chisq.test(x = obs, p = exp, rescale.p = TRUE)

  #Show result
  xsq <- data.frame("X_Square" = xsq$statistic,
                    "df" = xsq$parameter,
                    "p" = xsq$p.value)
  rownames(xsq) <- NULL

  return (xsq)
}
```

Conduct a Chi-square test for situational clustering

```{r}
# Chi-square for victimisation or offending
cacc_xsq(cacc_matrix_vict)
# cacc_xsq(cacc_matrix_offe)
```


# SCI analysis

Load the data prepare and sci functions

```{r}
# ---- data_prepare function ----
data_prepare <- function(cacc_matrix){
  #If the Break variable does not exist, cacc matrix is calculated.
  if(("N_Break" %in% names(cacc_matrix)) == FALSE){
    cacc_matrix <- cacc(cacc_matrix)
    print("CACC matrix has been calculated")
  }

  #If the entered dataset have the necessary variables to calculate
  #the Lorentz Curve, the following are not calculated
  if(("N_Break_D" %in% names(cacc_matrix)) == TRUE){
    return(cacc_matrix)
  }
  
  #Total configuration cases
  N <- nrow(cacc_matrix)

  #N_Break ordered from lowest to highest
  cacc_matrix <- cacc_matrix[order(cacc_matrix$N_Break, decreasing = TRUE), ]

  #Insert new row with total sum of N_Break
  vector <- c(rep(0, length(cacc_matrix)))  #Vector of zeros
  cacc_matrix <- rbind(vector, cacc_matrix) #Add vector into dataframe
  cacc_matrix$N_Break[1] <- sum(cacc_matrix$N_Break) #Sum N_Break

  #Cumulative N_Break
  cacc_matrix$N_Break_D <- 0 #Initialise column

  for(i in 1:N){
    if(i == 1){
      cacc_matrix$N_Break_D[i] <- cacc_matrix$N_Break[i]
      next
    }
    cacc_matrix$N_Break_D[i] <- cacc_matrix$N_Break_D[i - 1] - cacc_matrix$N_Break[i]
  }

  #%CFD of N_Break_D
  maxAcumulative <- cacc_matrix$N_Break[1]
  cacc_matrix$p_N_Break_D <- cacc_matrix$N_Break_D/maxAcumulative

  #Column Configs
  vector <- seq(from = 1, to = 0, length.out = N + 1)  #Vector of zeros
  cacc_matrix$Config <- vector

  #N?? of Configs
  vector <- N:0  #Vector of number case configurations
  cacc_matrix$num_Config <- vector

  #CDF % of Configs
  cacc_matrix$p_Configs <- cacc_matrix$num_Config/N


  #Area under L Curve
  cacc_matrix$L_Curve <- 0 #Initialise column

  for (i in 1:N){
    cacc_matrix$L_Curve[i] <- ((cacc_matrix$p_N_Break_D[i+1]+cacc_matrix$p_N_Break_D[i])/2)*(1/N)
  }


  return (cacc_matrix)
}

# ---- sci function ----
sci <- function(cacc_matrix){
  #If the Break variable does not exist, cacc matrix is calculated.
  if(("N_Break" %in% names(cacc_matrix)) == FALSE){
    cacc_matrix <- cacc(cacc_matrix)
    print("CACC matrix has been calculated")
  }

  #If the entered dataset does not have the necessary variables to calculate
  #the Lorentz Curve, the following are calculated
  if(("N_Break_D" %in% names(cacc_matrix)) == FALSE){
    #Prepare cacc_matrix to calculate Curve Lorenz
    cacc_matrix <- data_prepare(cacc_matrix)
    print("Dataset has been prepared")
  }

  #Sum L_Curve to calculate area L Curve
  area_L_Curve <- sum(cacc_matrix$L_Curve)

  #Area A
  A <- 0.5 - area_L_Curve

  #Area B
  B <- area_L_Curve/0.5

  SCI <- 1-B

  return (SCI)
}
```

Prepare each dataset to calculate the SCI aftwerwards

```{r}
# Prepare the victimisation or offending matrix
prepared_cacc_matrix_vict <- data_prepare(cacc_matrix_vict)
# prepared_cacc_matrix_offe <- data_prepare(cacc_matrix_offe)

# Calculate the SCI on any matrix
round(sci(prepared_cacc_matrix_vict), digits = 3)
# round(sci(prepared_cacc_matrix_offe), digits = 3)
```


# Homogeneous populations

```{r}
# Merge both CACC matrix
cacc_matrix_comb <- full_join(cacc_matrix_vict, 
                              cacc_matrix_offe, 
                              by = c("sex", "age_", "hours_", "privacy", "name", "photos", "snapchat", "instagram", "facebook", "twitter", "N_Break"),
                              copy = TRUE
                              )

# Rearrange the data for plotting
df_fig1 <- cacc_matrix_comb %>%
  select(p.y,
         p.x
         ) %>% 
  rename("p_offe" = p.y,
         "p_vict" = p.x
         ) %>% 
  mutate(id_vict = 1:nrow(cacc_matrix_comb)) %>% 
  arrange(desc(p_offe)) %>% 
  mutate(id_offe = 1:nrow(cacc_matrix_comb),
         id_diff = abs(id_vict - id_offe)) %>% 
  select(id_vict,
         id_offe,
         id_diff
         )

# Parallel plot
fig1 <- ggparcoord(data = df_fig1,
             columns = c(1, 2),
             groupColumn = "id_diff",
             scale = "robust",
             ) +
  scale_x_discrete(expand = c(0, 0),
                   labels = c("victimization \nranking", "offending \nranking")
                   ) +
  scale_y_reverse(expand = c(0, 0),
                  breaks = c(1, -1),
                  labels = c("lower \nprobability", "higher \nprobability")
                  ) +
  xlab(element_blank()) +
  ylab("Situational profiles (n = 94)") +
  scale_color_continuous(low = "lightgrey", 
                         high = "black", 
                         guide = guide_colourbar(title = "Ranking \nvariation",
                                                 ticks = TRUE,
                                                 label = TRUE,
                                                 barwidth = 0.5,
                                                 barheight = 12
                                                 )
                         ) +
  theme_minimal() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()
        )
print(fig1)
```


# Export the CACC tables

```{r}
# Victimization Table
write.xlsx(x = cacc_matrix_vict,
           file = "table_vict.xlsx"
           )

# Offending Table
write.xlsx(x = cacc_matrix_offe,
           file = "table_offe.xlsx"
           )

# Combined Table
write.xlsx(x = cacc_matrix_comb,
           file = "table_comb.xlsx"
           )
```

